\texttt{SuperScreen}: An open-source package for simulating the magnetic response of two-dimensional superconducting devices

### 2022-01-18 main.tex
Updates from Overleaf

\SuperScreen has several important dependencies beyond the Python standard library: \inline{numpy}~\cite{Harris2020-xv} and \inline{scipy}~\cite{Virtanen2020-zz} for numerics, \inline{matplotlib}~\cite{Hunter2007-il} for visualization, \inline{pint}~\cite{Grecco} for handling physical units, \inline{shapely}~\cite{shapely} for creating and manipulating device geometries, \inline{meshpy}~\cite{Klockner, Shewchuk, Shewchuk1996-va} and \inline{optimesh}~\cite{Schlomer2021-ua} for mesh generation, and \inline{ray}~\cite{Moritz2018-mt,ray-docs} for parallel processing with shared memory (see~\ref{section:parallel}).

@@

To include vortices in a \SuperScreen model, one can simply input a \inline{list} of \inline{superscreen.Vortex} objects when calling \inline{superscreen.solve()}. A \inline{Vortex} object specifies the $x,y$ position for the vortex core, the name of the superconducting layer in which the vortex is pinned, and the number of flux quanta $\Phi_0$ contained in the vortex (which is 1 by default). The field distributions generated by \SuperScreen in the presence of vortices as described in Sections~\ref{section:model:vortices} and~\ref{section:implementation} agree to within a few percent with the distributions obtained using this Fourier transform method, as demonstrated in Figure~\ref{fig:pearl}(c-e). Figure~\ref{fig:pearl}({\bf e}) shows the fluxoid for a circular region $S$ with radius $r=1\,\um$ enclosing a Pearl vortex trapped in a film as a function of the film's effective penetration depth, $\Lambda$. When $\Lambda=0$, the screening currents decay very quickly away from the center of the vortex, so the ``supercurrent part'' of the $\Phi^f_S$ vanishes. With increasing $\Lambda$, the ``supercurrent part'' accounts for an increasing fraction of the total fluxoid. See Ref.~\cite{Brandt2005-wj} for a method to compute the self-energy and interaction energies of vortices in thin films.

@@

\section{Parallel processing}
\label{section:parallel}
As discussed above, one can solve many models involving the same \inline{Device} in parallel across multiple CPUs using the \inline{superscreen.solve_many()} function. The recommended method for parallel processing is using \inline{ray}, a library for distributed computing using shared memory~\cite{Moritz2018-mt}. Note that at the time of writing, \inline{ray} support for Windows is experimental and under active development. \SuperScreen also supports parallel processing using the \inline{multiprocessing} module from the Python standard library, however this is generally less efficient than \inline{ray} in this application.

\begin{code}
\begin{minted}[fontsize=\small]{python}
# Assume that we have already created a Device and put all
# other inputs to superscreen.solve_many() into a dictionary
# called other_kwargs.

import psutil
import ray

@@

# Start a ray cluster
ray.init(num_cpus=num_cpus)
# Solve the models
solutions, paths = superscreen.solve_many(
    parallel_method="ray",
    **other_kwargs,
)
# Shutdown the ray cluster
ray.shutdown()
\end{minted}
\captionof{listing}{Starting and stopping \inline{ray} outside of \inline{superscreen.solve_many()} using the Python API. See the ``API and Package Reference" section of the \inline{ray} documentation for additional options in \inline{ray.init()}~\cite{ray-docs}.}
\label{code:ray-python}
\end{code}

\begin{code}
\begin{minted}[fontsize=\small]{bash}
# Start a ray cluster from the command line, e.g. bash
ray start --head --num-cpus=3
\end{minted}
\begin{minted}[fontsize=\small]{python}
# Assume that we have already created a Device and put all
# other inputs to superscreen.solve_many() into a dictionary
# called other_kwargs.
import ray
# Connect to the existing ray cluster.
# If more than one ray cluster is running, specify
# which to connect to using address="{ip}:{port}".
ray.init(address="auto")
# Solve the models.
solutions, paths = superscreen.solve_many(
    parallel_method="ray",
    **other_kwargs,
)
\end{minted}
\begin{minted}[fontsize=\small]{bash}
# Shut down the ray cluster from the command line
ray stop
\end{minted}
\captionof{listing}{Starting and stopping \inline{ray} outside of \inline{superscreen.solve_many()} using the command line interface. See the \inline{ray} documentation for additional options in \inline{ray start}~\cite{ray-docs}.}
\label{code:ray-cli}
\end{code}

There are three ways to invoke \inline{ray} from \SuperScreen when running on a single machine, e.g. a multi-core CPU. The first is to simply pass the keyword argument \inline{parallel_method="ray"} when calling \inline{solve_many()}. This will automatically create a \inline{ray} cluster using all available physical CPU cores, solve the models in parallel, and then shut down the cluster before returning. The second method is to manually create a \inline{ray} cluster using the \inline{ray} Python application programming interface (API) prior to calling \inline{solve_many(..., parallel_method="ray")}, as demonstrated in Code Block~\ref{code:ray-python}. The third method is to start a \inline{ray} cluster using the command line interface (CLI), then connect to the existing cluster using the Python API prior to calling \inline{solve_many(..., parallel_method="ray")}, as demonstrated in Code Block~\ref{code:ray-cli}. One of the latter two methods should be used for finer control over the \inline{ray} cluster (number of CPUs to utilize, etc.).

Running \inline{superscreen.solve_many()} in parallel across multiple nodes in a computing cluster is a simple extension to the method outlined in Code Block~\ref{code:ray-cli}, although the specifics depend upon the infrastructure of the cluster, e.g. job management software. See the ``Multi-Node Ray" section of the \inline{ray} documentation for more details~\cite{ray-docs}.
% Some applications of \SuperScreen may be ``embarrassingly parallel'' in the sense that all calls to \inline{superscreen.solve()} are completely independent. One such application is the scanning SQUID susceptometry simulation shown in Section~\ref{section:application}. In such cases, it may be simpler to avoid using \inline{ray} for shared memory and run many

>>>>

\SuperScreen has several important dependencies beyond the Python standard library: \inline{numpy}~\cite{Harris2020-xv} and \inline{scipy}~\cite{Virtanen2020-zz} for numerics, \inline{matplotlib}~\cite{Hunter2007-il} for visualization, \inline{pint}~\cite{Grecco} for handling physical units, \inline{shapely}~\cite{shapely} for creating and manipulating device geometries, \inline{meshpy}~\cite{Klockner, Shewchuk, Shewchuk1996-va} and \inline{optimesh}~\cite{Schlomer2021-ua} for mesh generation, and \inline{Ray}~\cite{Moritz2018-mt,ray-docs} for parallel processing with shared memory (see~\ref{section:parallel}).

@@

To include vortices in a \SuperScreen model, one can simply input a \inline{list} of \inline{superscreen.Vortex} objects when calling \inline{superscreen.solve()}. A \inline{Vortex} object specifies the $x,y$ position for the vortex core, the name of the superconducting layer in which the vortex is pinned, and the number of flux quanta $\Phi_0$ contained in the vortex (which is 1 by default). The field distributions generated by \SuperScreen in the presence of vortices as described in Sections~\ref{section:model:vortices} and~\ref{section:implementation} agree to within a few percent with the distributions obtained using this Fourier transform method, as demonstrated in Figure~\ref{fig:pearl}. Figure~\ref{fig:pearl}({\bf e}) shows the fluxoid for a circular region $S$ with radius $r=1\,\um$ enclosing a Pearl vortex trapped in a film as a function of the film's effective penetration depth, $\Lambda$. When $\Lambda=0$, the screening currents decay very quickly away from the center of the vortex, so the ``supercurrent part'' of the $\Phi^f_S$ vanishes. With increasing $\Lambda$, the ``supercurrent part'' accounts for an increasing fraction of the total fluxoid. See Ref.~\cite{Brandt2005-wj} for a method to compute the self-energy and interaction energies of vortices in thin films.

@@

\section{Parallel processing}
\label{section:parallel}
As discussed above, one can solve many models involving the same \inline{Device} in parallel across multiple CPUs using the \inline{superscreen.solve_many()} function. There are two methods available for process-based parallelism in \SuperScreen: \inline{parallel_method="multiprocessing"}, which uses the \inline{multiprocessing} package from the Python standard library, and \inline{parallel_method="ray"}, which uses the third-party distributed computing framework \inline{Ray}\footnote{Note that at the time of writing, \inline{Ray} support for Windows is experimental and under active development.}~\cite{Moritz2018-mt,ray-docs}. Both approaches utilize shared memory so that only a single copy is made of the large arrays required to solve a \inline{Device} (the mesh, kernel matrix $\mathbf{Q}$, Laplace operator $\mathbf{\nabla}^2$, etc.), rather than \inline{num_cpus} copies, where \inline{num_cpus} is the number of worker processes.

\begin{code-onecol}
\begin{minted}[fontsize=\small]{python}
parallel_method = "multiprocessing"
# parallel_method = "ray"

# Specify number of worker processes:
num_cpus = 4
# Or automatically use all
# available physical CPUs:
# num_cpus = None

_ = superscreen.solve_many(
    device=device,
    parallel_method=parallel_method,
    num_cpus=num_cpus,
    **solve_kwargs,
)
\end{minted}
\captionof{listing}{Utilizing process-based parallelism in \SuperScreen given a \inline{superscreen.Device} and solver options stored in a dictionary \inline{solve_kwargs}.}
\label{code:parallel}
\end{code-onecol}

There are three ways to invoke \inline{Ray} from \SuperScreen when running on a single machine, e.g. a multi-core CPU. The first is to simply pass the keyword argument \inline{parallel_method="ray"} when calling \inline{solve_many()} (see Code Block~\ref{code:parallel}). This will automatically create a \inline{Ray} cluster using (by default) all available physical CPU cores, solve the models in parallel, and then shut down the cluster before returning. The second method is to manually create a \inline{Ray} cluster using the \inline{Ray} Python application programming interface (API) prior to calling \inline{solve_many(..., parallel_method="ray")}, as demonstrated in Code Block~\ref{code:ray-python}. The third method is to start a \inline{Ray} cluster using the command line interface (CLI), then connect to the existing cluster using the Python API prior to calling \inline{solve_many(..., parallel_method="ray")}, as demonstrated in Code Block~\ref{code:ray-cli}. One of the latter two methods should be used for finer control over the \inline{Ray} cluster. For example, if calling \inline{solve_many()} many times in a single session, one can use these methods to avoid the overhead of starting and stopping a \inline{Ray} cluster multiple times.

Running \inline{superscreen.solve_many()} in parallel across multiple nodes in a computing cluster is a simple extension to the method outlined in Code Block~\ref{code:ray-cli}, although the specifics depend upon the infrastructure of the cluster, e.g. job management software. See the ``Multi-Node Ray" section of the \inline{Ray} documentation for more details~\cite{ray-docs}.

\begin{code}
\begin{minted}[fontsize=\small]{python}
# Assume that we have already created a Device and put all other inputs
# to superscreen.solve_many() into a dictionary called other_kwargs.
import psutil
import ray

@@

# Start a ray cluster
ray.init(num_cpus=num_cpus)
# Solve the models
solutions, paths = superscreen.solve_many(
    parallel_method="ray",
    **other_kwargs,
)
# Potentially call solve_many() again using the same ray cluster...
# Finally, shutdown the ray cluster
ray.shutdown()
\end{minted}
\captionof{listing}{Starting and stopping \inline{Ray} outside of \inline{superscreen.solve_many()} using the Python API. See the ``API and Package Reference" section of the \inline{Ray} documentation for additional options in \inline{ray.init()}~\cite{ray-docs}.}
\label{code:ray-python}
\end{code}

\begin{code}
\begin{minipage}{1.0\textwidth}
\begin{minted}[fontsize=\small]{bash}
# Start a ray cluster from the command line, e.g. bash
ray start --head --num-cpus=3
\end{minted}

\begin{minted}[fontsize=\small]{python}
# Assume that we have already created a Device and put all other inputs
# to superscreen.solve_many() into a dictionary called other_kwargs.
import ray
# Connect to the existing ray cluster.
# If more than one ray cluster is running, specify
# which to connect to using address="{ip}:{port}".
ray.init(address="auto")
# Solve the models.
solutions, paths = superscreen.solve_many(
    parallel_method="ray",
    **other_kwargs,
)
# Potentially call solve_many() again using the same ray cluster...
\end{minted}

\begin{minted}[fontsize=\small]{bash}
# Shut down the ray cluster from the command line
ray stop
\end{minted}
\captionof{listing}{Starting and stopping \inline{Ray} outside of \inline{superscreen.solve_many()} using the command line interface. See the \inline{Ray} documentation for additional options in \inline{ray start}~\cite{ray-docs}.}
\label{code:ray-cli}
\end{minipage}
\end{code}
